---
title: ""
author: "H. Emre Etlioglu"
format:
  html:
    self-contained: true
    toc: true
    code-fold: true
    code-summary: "Show the code"
    page-layout: full
editor: visual
---

# RNA-seq

The `AzureDevops` repo for this project is located [here](lin-to-the-git-repo) and contains all of the code as well as input and output data, with the exception of large raw data files, which are stored in `Stor9`.

## Info on this report

### Report version:

version-1.0-YYYY-MM-DD

### What is different from the previous version

### About the analyses performed

The heavy lifting is mainly done by `DESeq2` and this report closely resembles its following vignettes:

-   [RNA-seq workflow: gene-level exploratory analysis and differential expression](http://master.bioconductor.org/packages/release/workflows/vignettes/rnaseqGene/inst/doc/rnaseqGene.html)
-   [Analyzing RNA-seq data with DESeq2](https://bioconductor.org/packages/release/bioc/vignettes/DESeq2/inst/doc/DESeq2.html)

## Info on the project

### To-do

### Questions to the researchers

### Hypothesis/Questions from the researchers

Contrasts to be performed:

## Set-up

```{r set-up}

library(ggplot2)

# customize ggplot
source("https://raw.githubusercontent.com/etlioglu/bioinformatics/main/templates/customize-ggplot.r")
```

## 2. Input to DESeq2

### 2.1 Read count generation

### 2.2 Count data

```{r count-data}

count_df <- read.delim("preprocessing/nextflow-output/star_salmon/salmon.merged.gene_counts_length_scaled.tsv")
rownames(count_df) <- count_df[, 1]

# get rid of the first two columns: ENSEMBL identifiers and gene names
count_df[, 1:2] <- NULL

# integers are required for the downstream applications
count_df <- round(count_df)
```

### 2.3 Sample meta-data

### 2.4 Gene meta-data

## 3.4 DESeq2 object creation

## 4. Exploratory data analysis

### 4.1 Pre-filtering

### 4.2 variance stabilizing transformation

```{r vst}

vsd <- vst(dds, blind = TRUE)
```

### 4.3 Sample distances

### 4.4 PCA Plots

#### 4.4.1 Non-interactive

#### 4.4.2 Interactive

## 5. Differential expression analysis

## 6 Session Info

```{r session-info}

sessionInfo()
```
