---
title: ""
author: "H. Emre Etlioglu"
format:
  html:
    self-contained: true
    toc: true
    code-fold: true
    code-summary: "Show the code"
    page-layout: full
editor: visual
---

## RNA-seq

### Report version: 1.0

### What is different from the previous version

### About the analyses performed

The heavy lifting is mainly done by `DESeq2` and this report closely resembles its following vignettes:

-   [RNA-seq workflow: gene-level exploratory analysis and differential expression](http://master.bioconductor.org/packages/release/workflows/vignettes/rnaseqGene/inst/doc/rnaseqGene.html)
-   [Analyzing RNA-seq data with DESeq2](https://bioconductor.org/packages/release/bioc/vignettes/DESeq2/inst/doc/DESeq2.html)

## 0. Set-up

```{r set-up}

library(ggplot2)

# customize ggplot
source("https://raw.githubusercontent.com/etlioglu/bioinformatics/main/templates/customize-ggplot.r")
```

```{r customize-plots}

gradient_col_palette <- viridis(100)

# from scCustomize::ColorBlind_Pal()
large_disc_col_pal <-
  c(
    "#F0A0FFFF",
    "#0075DCFF",
    "#993F00FF",
    "#4C005CFF",
    "#191919FF",
    "#005C31FF",
    "#2BCE48FF",
    "#FFCC99FF",
    "#808080FF",
    "#94FFB5FF",
    "#8F7C00FF",
    "#9DCC00FF",
    "#C20088FF",
    "#003380FF",
    "#FFA405FF",
    "#FFA8BBFF",
    "#426600FF",
    "#FF0010FF",
    "#5EF1F2FF",
    "#00998FFF",
    "#E0FF66FF",
    "#740AFFFF",
    "#990000FF",
    "#FFFF80FF",
    "#FFE100FF",
    "#FF5005FF"
  )

options(ggplot2.discrete.colour = large_disc_col_pal)
theme_set(theme_bw())
```

## 1. Introduction

### 1.1 Questions/hypotheses from the researcher

Contrasts to be performed:

## 2. Input to DESeq2

### 2.1 Read count generation

### 2.2 Count data

### 2.3 Sample meta-data

### 2.4 Gene meta-data

## 3.4 DESeq2 object creation

## 4. Exploratory data analysis

### 4.1 Pre-filtering

### 4.2 variance stabilizing transformation

```{r vst}

vsd <- vst(dds, blind = TRUE)
```

### 4.3 Sample distances

### 4.4 PCA Plots

#### 4.4.1 Non-interactive

#### 4.4.2 Interactive

## 5. Differential expression analysis

## 6 Session Info

```{r session-info}

sessionInfo()
```
